Tree height and hydraulic traits shape growth responses across droughts in a temperate broadleaf forest

### 2020-01-31 manuscript/tables&figures.Rmd
update Table 1
altered presenation of hypotheses and sub-hypotheses (issue #67), visual cleanup

```{r Table 1, eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
hypothesis_table <- read.csv("tables_figures/table1_hypothesis_table.csv", stringsAsFactors = FALSE, check.names = FALSE)
kable(hypothesis_table, booktabs = TRUE, caption = "**Table 1. Summary of hypotheses, corresponding specific predictions, and results.** We count predictions as fully supported ('yes') when the response is signficant in univariate models and included in all top multivariate models and as partially supported ('yes') when the direction of response consistently matched the prediction but  the effect was not significant in all models.") %>%
  pack_rows("Hypothesis 1: Tree height is the dominant size-related variable affecting drought resistance (Rt)", 1, 5, latex_gap_space = "1em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("1a. Larger, taller trees have lower Rt.", 1, 2, latex_gap_space = "1em", colnum = 1, hline_before = FALSE, bold = FALSE, italic = TRUE) %>%
  pack_rows("1b. Trees with more exposed crowns have lower Rt.", 3, 4, latex_gap_space = "1em", colnum = 1, hline_before = FALSE, bold = FALSE, italic = TRUE) %>%
  pack_rows("1c. Small trees (lower root volume) in drier microhabitats have lower Rt.", 5, 5, latex_gap_space = "1em", colnum = 1, hline_before = FALSE, bold = FALSE, italic = TRUE) %>%
  pack_rows("Hypothesis 2: Species' traits--particularly leaf hydraulic traits--predict Rt", 6, 10, latex_gap_space = "1em", colnum = 1, hline_before = TRUE) %>%
  add_header_above(c(" ", "Prediction supported?" = 4, " ")) %>%
  column_spec(1, width = "12cm") %>%
  column_spec(2:5, width = "1.2cm") %>%
  column_spec(6, width = "2.4cm") %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), font_size = 8.5) %>%
  kableExtra::landscape()
```
\clearpage

>>>>

```{r Table 1, eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
hypothesis_table <- read.csv("tables_figures/table1_hypothesis_table.csv", stringsAsFactors = FALSE, check.names = FALSE)
kable(hypothesis_table, booktabs = TRUE, caption = "**Table 1. Summary of hypotheses, corresponding specific predictions, and results.** We count predictions as fully supported ('yes') when the response is signficant in univariate models and included in all top multivariate models and as partially supported ('yes') when the direction of response consistently matched the prediction but  the effect was not significant in all models.") %>%
  pack_rows("Tree size and microenvironment", 1, 5, latex_gap_space = "1em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("1a. Larger, taller trees have lower Rt.", 1, 2, latex_gap_space = "1em", colnum = 1, hline_before = FALSE, bold = FALSE, italic = TRUE) %>%
  pack_rows("1b. Trees with more exposed crowns have lower Rt.", 3, 4, latex_gap_space = "1em", colnum = 1, hline_before = FALSE, bold = FALSE, italic = TRUE) %>%
  pack_rows("1c. Small trees (lower root volume) in drier microhabitats have lower Rt.", 5, 5, latex_gap_space = "1em", colnum = 1, hline_before = FALSE, bold = FALSE, italic = TRUE) %>%
  pack_rows("Species traits", 6, 10, latex_gap_space = "1em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("2. Species' traits--particularly leaf hydraulic traits--predict Rt.", 6, 10, latex_gap_space = "1em", colnum = 1, hline_before = FALSE, bold = FALSE, italic = TRUE) %>%
  add_header_above(c(" ", "Prediction supported?" = 4, " ")) %>%
  column_spec(1, width = "12cm") %>%
  column_spec(2:5, width = "1.2cm") %>%
  column_spec(6, width = "2.4cm") %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), font_size = 8.5) %>%
  kableExtra::landscape()
```
\clearpage
